Embodied Neuromorphic Benchmarks

### 2015-08-08 paper/paper.tex
sim versus phys

We believe embodied benchmarks should be of particular interest to
neuromorphic research, given that many of the applications of neuromorphic
hardware are in exactly this domain of embedded and interactive control
of robotic or other physical systems.  However, embodiment raises a number
of issues that complicate the development of such benchmarks.  Rather than
simply providing a data file of inputs and desired outputs, the benchmark
must either specify a full physical system for that embodiment, or it must 
provide software for a simulation of that system.  As we discuss below, either
approach is problematic, and addressing this problem is the primary goal of
this paper.

@@

@@

>>>>

We believe embodied benchmarks should be of particular interest to
neuromorphic research, given that many of the applications of neuromorphic
hardware are in exactly this domain of embedded and interactive control
of robotic or other physical systems.  However, embodiment raises a number
of issues that complicate the development of such benchmarks.  Rather than
simply providing a data file of inputs and desired outputs, the benchmark
must either specify a full physical system for that embodiment, or it must 
provide software for a simulation of that system.  As we discuss below, either
approach is problematic, and addressing this difficulty is the primary goal of
this paper.

@@

An embodied benchmark task is one where the system we are studying has a 
two-way interaction with some sort of environment.  That is, the outputs from
the neuromorphic hardware are sent to the environment where they cause some
sort of effect, the results of which change the subsequent input.  For example,
the outputs might control the movement of a robot, which in turn affects the
sensory data received by the robot.

@@

To define such a benchmark, we need to be explicit about the embodiment.  If
it is a situation where a robot is to be controlled, we need to be explicit
about all the details of that robot.  What motors are there?  How are they
configured?  How strong are they?  What sensors are there?  Where are they
placed?  How accurate are they?  However, even if these questions are
answered, there is a fundamental problem in that \emph{other researchers
need access to that exact robot}.  If a benchmark is to be widely used, other
researchers developing their own hardware should be able to do their own 
testing.

Furthermore, using a physical robot also imposes significant practical
difficulties when performing extensive benchmark testing.  When testing, we
often want to run the same task over and over again, both for robustness and
to see the effects of varying parameters.  With a physical robot, this means
manually setting up the task, letting the test run, gathering the resulting
data, and then resetting the robot back to the initial state.  This means that
issues like battery life become problematic, and not just because there is a
limited amount of time available for testing.  As the battery level changes,
the performance of the robot itself can also change.  Futhermore, for any
rigorous testing of the benchmark, we will want to examine situations where
the system fails.  This means that some of the testing will involve parameter
settings that lead to poor behaviour, which could involve physical damage to
the robot itself.

However, \emph{not} using a real physical embodiment for testing is also
problematic.  First and foremost, without an actual real-world task, why
should anyone have any confidence that the performance on the benchmark is
reflective of the actual usefulness of the neuromorphic hardware?  It is
very widely known that \emph{simulations of robots} (or other physical systems) are
often much easier to control and better-behaved than the real thing.  The
field of robotics is filled with algorithms that work well ``in theory'', but
fail when run on actual hardware.  We do not want a benchmark that falls into
this trap of failing to generalize to real situations.

Furthermore, neuromorphic hardware has another constraint that severely limits
the possibilities of simulation.  The normal approach when a simulation is
too simple to reflect reality is to add details to the simulation itself.
Incredibly finely detailed simulations can be created, filling in all of the
details needed.  However, those resulting simulations \emph{cannot be run
in real-time}.  This is a fundamental problem, in that most neuromorphic
hardware is about real-time interactions, and there is no way to slow down
the hardware to match the simulated environment.  This means that even if
we spent the considerable amount of research effort needed to define a
simulated environment for an embodied benchmark, that simulation could not
be run fast enough to interact with most of the hardware that we would want
to test.
